\documentclass[11pt,letterpaper]{article}

\usepackage{subfigure}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumitem}

\setlength{\textwidth}{6.5in}     
\setlength{\oddsidemargin}{0in}  
\setlength{\evensidemargin}{0in}
\setlength{\textheight}{8.5in} 
\setlength{\topmargin}{0in}   
\setlength{\headheight}{14pt} 
\setlength{\headsep}{10pt}   
%\setlength{\footskip}{0in}

%------------------------------------------------
\newcommand{\homework}[2]{
\setcounter{section}{#1}
\section*{ICS621 Homework {\thesection}: {#2} }
{\markboth{#2}{#2}}
}
%------------------------------------------------


 \addtolength{\parskip}{\baselineskip}
\begin{document}

% Enter the Homework number and title as arguments to
% homework
\homework{3}{Bucket Sort on a Circle or Water Jugs}

\noindent Choose one of the following.

\noindent
\textbf{Problem 8.4-4 from CLRS.} 
We are given $n$ points in the unit circle, $p_i=(x_i,
y_i)$, such that $0< x_i^2+y_i^2 \leq 1$ for
$i=1,2,\ldots,n$. Suppose that the points are uniformly
distributed; that is, the probability of finding a point in
any region of the circle is proportional to the area of that
region. Design an algorithm with an average-case running
time of $\Theta(n)$ to sort the $n$ points by their distance
$d_i=\sqrt{x_i^2+y_i^2}$ from the origin. (\textit{Hint:}
Design the bucket sizes in Bucket-Sort to reflect the
uniform distribution of the points in the unit circle.)

\noindent
\textbf{Problem 8-4 from CLRS.} 
Suppose that you are given $n$ red and $n$ blue water jugs,
all of different shapes and sizes. All red jugs hold
different amounts of water, as do the blue ones. Moreover,
for every red jug, there is a blue jug that holds the same
amount of water, and vice versa. Your task is to find a
grouping of the jugs into pairs of red and blue jugs that
hold the same amount of water. To do so, you may perform the
following operation: pick a pair of jugs in which one is
red and one is blue, fill the red jug with water, and then
pour the warer into the blue jug. This operation will tell
you whether the red or the blue jug can hold more water, or
they have the same volume. Assume that such a comparison
takes one time unit. Your goal is to find an algorithm that
makes a minimum number of comparisons to determine the
grouping. Remember that you may not directly compare two red
jugs or two blue jugs.
\begin{enumerate}[label=\alph*),labelindent=0pt]
\item Describe a deterministic algorithm that uses
$\Theta(n^2)$ comparisons to group the jugs into pairs.
\item Prove a lower bound of $\Omega(n \lg n)$ for the
number of comparisons that an algorithm solving this problem
must make.
\item Give a randomized algorithm whose expected number of
comparisons is $O(n \lg n)$, and prove that this bound is
correct. What is the worst-case number of comparisons for
your algorithm?
\end{enumerate}

\end{document}
